---
title: "12/01 scratchpad"
output: html_notebook
---

## part one 

```{r}
td1 <- data.table::fread(file = here::here('tests', 'data', 'day_01'),
                         header = FALSE)
dd1 <- data.table::fread(file = here::here('data', 'day_01'),
                         header = FALSE)

```

We need the output of `insert function here` applied to `td1` to be `c(12, 38, 15, 77)` summed to `142`. 

I assume that `treb7chet` turning into `77` means that the first digit gets to also count as the last digit.

```{r}
td1[, n := stringr::str_remove_all(V1, '\\D')]
td1[, fi := stringr::str_sub(n, 1, 1)]
td1[, la := stringr::str_sub(n, -1)]
td1[, res := paste0(fi, la)]
sum(td1$res |> as.numeric())
```
Well at least the test works. This has *got* to be the kludgiest way possible but finals week gonna do that to me.

Let's make some generics.

And figure out how the fuck `rprojroot` works so I can stop my shameful `here` kludges... maybe.

Update: hrghhh no there's just *no* documentation that tells me the part of this I mean, I don't know what I'm doing wrong? I would ask SO but that's where the RSD lives and this is *basic `rprojroot` intended usage*, I don't know where they're *hiding* it is all? 

```{r}
take_input <- \(day = 1, pt = 'a', ...) { #use ... to make tests work, for now
  if (day <= 10) day = paste0(0, day) #this is so bad, oh my G-d.
  if (pt != 'a') day = paste0(day, pt) #haven 't done this before, unsure how to handle second part
  day = paste0('day_', day) #why did I opt for this file name convention anyway
  using_path <- here::here(..., 'data', day) #why won't rprojroot explain how to stop doing this
  data.table::fread(file = using_path, header = FALSE) #oh well at least it works 
}
```

This is. So bad. This is terrible. Oh well

```{r}
filter_calibration <- \(dt) {
  dt[, n := stringr::str_remove_all(V1, '\\D')]
  dt[, res := 
       paste0(stringr::str_sub(n, start = 1, end = 1),
              stringr::str_sub(n, start = -1))]
  dt$res |> as.numeric()
}

cal_res <- \(dt) {
  sum(filter_calibration(dt))
}
```


## part two

```{r}
bd1 <- take_input(day = 1, pt = 'b', 'tests')
```
```{r}
fix_written <- \(dt) {
  vec <- dt$V1 |> as.character()
  vec <- stringr::str_replace_all(vec, 'one', '1') |>
    stringr::str_replace_all('two', '2') |>
    stringr::str_replace_all('three', '3') |>
    stringr::str_replace_all('four', '4') |>
    stringr::str_replace_all('five', '5') |>
    stringr::str_replace_all('six', '6') |>
    stringr::str_replace_all('seven', '7') |>
    #seriously, it's R, there's GOT to be utilities to make this conversion already
    stringr::str_replace_all('eight', '8') |>
    stringr::str_replace_all('nine', '9')
  vec
}
```

We want the output for `bd1` to be `29`, `83`, `13`, `24`, `42`, `14`, `76`.

```{r}
bd1_fix <- fix_written(bd1)
```

Ah for fuck's sake.

Come back in a bit and figure out how to fix the precedence there, then.

```{r}
num_eng <- c('one', 'two', 'three', 'four', 'five', 'six', 'seven', 'eight', 'nine') 
loi <- strsplit(num_eng, split = '') |> 
  unlist(recursive = FALSE) |> wrapr::uniques()
choi <- c(loi, 1:9) #all characters of interest
# stringr::str_extract_all(string = bd1$V1[1], pattern = choi) 
## yeah that doesn't do what I want either 
```

```{r}
bd1[, ch := stringr::str_flatten(stringr::str_extract_all(V1, pattern = '[onetwhrfuivsxg123456789
]'), collapse = '')]

t <- bd1$V1
str_extract_all(t, pattern = '[onetwhrfuivsxg123456789]')

```
```{r}
# first letters of interest
fli <- '[otfsen]'
lli <- '[eorxnt]'
sdn <- list(one = 1, two = 2, three = 3,
            four = 4, five = 5, six = 6,
            seven = 7, eight = 8, nine = 9)
kludge <- \(vec) {
  if (str_starts(string = vec, pattern = '\\d')) x <- vec[1]
  if (str_starts(string = vec, pattern = '[otfsen]')) {
    x <- vec[1:5] 
    x <- stringr::str_flatten(x, na.rm = TRUE)
  }
}
```
```{r}
str_starts(string = t, pattern = fli)
str_sub_all(t, start = -5, end = -1)
```
```{r}
t <- str_remove_all(string = t, pattern = '[^onetwhrfuivsxg123456789]')
tff <- stringr::str_sub(string = t, start = 1, end = 5)
tlf <- stringr::str_sub(string = t, start = -5, end = -1)

str_sub(string = tff[stringr::str_starts(string = tff, pattern = '\\d')], start = 1, end = 1)
str_extract(string = t, pattern = pat)

pat <- '1|2|3|4|5|6|7|8|9|one|two|three|four|five|six|seven|eight|nine'
tap <- stringi::stri_reverse(pat)
firsts <- str_extract(string = t, pattern = pat)
dd1[, first := str_extract(string = V1, pattern = pat)]
dd1[, rev := stringi::stri_reverse(V1)]
dd1[, last := str_extract(string = rev, pattern = tap)]
dd1[, last := stringi::stri_reverse(last)]
nums <- data.table(n = 1:9,
                   front = names(sdn),
                   back = stringi::stri_reverse(names(sdn)))
dd1[first == 'one', first := 1]
dd1[first == 'two', first := 2] #I KNOW there's an easier way to do this but I'm finals

setkey(nums, front)
dd1[, first := stringr::str_replace_all(first, c(one = '1', two = '2', three = '3',
                                                 four = '4', five = '5', six = '6', 
                                                 seven = '7', eight = '8', nine = '9'))]
dd1[, last := stringr::str_replace_all(last, c(one = '1', two = '2', three = '3',
                                                 four = '4', five = '5', six = '6', 
                                                 seven = '7', eight = '8', nine = '9'))]
dd1[, res := as.numeric(paste0(first, last))]
sum(dd1$res)
# kludge <- \(vec) {
  #res <- list(first = 0, last = 0)

#    if (stringr::str_starts(string = try, pattern = '\\d')) first <- stringr::str_sub(try, start = 1, end = 1)
#    if (stringr::str_ends(string = try, pattern = '\\d')) last <- stringr::str_sub(try, start = -1, end = -1)
#    ff <- stringr::str_sub(string = try, start = 1, end = 5)
#}
```

