---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rvest)
```

```{r}
input <- \(day = 1, year = 2023) {
  rvest::session('https://adventofcode.com/{year}/day/{day}/input',
                 year = year, day = day)
  rvest::html_elements()
}
# Well, that got a 400, so onwards.
```

TODO:
- Format for game data 
- Reformat to fit game data

What am I to consider an **observation**? -- One round of one game (has features GAME, RED, GREEN, BLUE, ROUND). 

```{r}
games <- readLines(con = here::here('data', 'day_02'))
```

```{r}
names(games) <- 1:100
```
```{r}
games <- stringr::str_remove_all(string = games, pattern = 'Game \\d+: ')
```
```{r}
rounds <- stringr::str_split(string = games, pattern = '; ')
```
```{r}
split_color <- \(round) {
  res <- stringr::str_split(string = round, pattern = ', ')
  res
}
```
```{r}
test_game <- split_color(rounds[[1]])
test_count <- str_extract_all(string = test_game, pattern = '\\d+')
test_color <- str_extract_all(string = test_game, pattern = 'red|blue|green')

# wrapr::named_map_builder(targets = test_color[[]], values = test_count)
test_color[[1]][1]

# as.character(test_color[]) %>% str_replace_all(pattern = 'c|((|))|,', replacement = '')
## mmmyeah no pe 
```

```{r}
name_color <- \(colors, counts) {
#  names(counts) <- colors
#  counts
  wrapr::named_map_builder(targets = colors, values = counts)
}
```

What I need at current format is rounds[[i]][j] (e.g. for Game 1 Round 1 rounds[[1]][1] will render me one list 'red' 'green' 'blue' one list '10' '7' '3')
```{r}
count_color <- \(vec) {
  color_ordered <- stringr::str_extract_all(string = vec, pattern = 'red|blue|green',
                                            simplify = TRUE) 
  count_ordered <- stringr::str_extract_all(string = vec, pattern = '\\d+',
                                            simplify = TRUE) 
#  furrr::future_map2(.x = color_ordered, .y = count_ordered, .f = name_color) 
  ### that works but I don't think it's working in parallel as intended, so...
#  list(colors = color_ordered, counts = count_ordered) ## so THAT works as intended once simplified...
  ### the fuck definition of 'simple' are we using here
#  wrapr::as_named_list(color_ordered, count_ordered)
#  name_color(colors = color_ordered, counts = count_ordered)
  res <- count_ordered
  names(res) <- color_ordered
  res
}
```

No that's sideways. Why can't I figure out how not to give myself things sideways.

Update: well at least it's not-sideways in the wrong way instead of just sideways.


```{r}
test_game <- rounds[[1]]
comp_colors <- stringr::str_extract_all(string = test_game, pattern = 'red|blue|green')
comp_counts <- stringr::str_extract_all(string = test_game, pattern = '\\d+')

test_colors <- comp_colors[[1]]
test_counts <- comp_counts[[1]]
names(test_counts) <- test_colors
test_counts
```
So... *that* works as intended. 

```{r}
count_color2 <- \(vec) {
  color_ordered <- stringr::str_extract_all(string = vec, pattern = 'red|blue|green',
                                            simplify = FALSE) 
  count_ordered <- stringr::str_extract_all(string = vec, pattern = '\\d+',
                                            simplify = FALSE) 
#  furrr::future_map2(.x = color_ordered, .y = count_ordered, .f = name_color) 
  ### that works but I don't think it's working in parallel as intended, so...
#  list(colors = color_ordered, counts = count_ordered) ## so THAT works as intended once simplified...
  ### the fuck definition of 'simple' are we using here
#  wrapr::as_named_list(color_ordered, count_ordered)
#  name_color(colors = color_ordered, counts = count_ordered)
  res <- count_ordered
  names(res) <- color_ordered
  res
}
```
...But **this** doesn't...

So I need to do for loops for now. Gross.

TODO: for loops I **guessss**

also my hand to G-d I could do this more elegantly  with lookaheads and capturing groups if I weren't [insert the usual excuses I am so tired please send help and caffeine it is finals]

```{r}
### This worked: 
# test_game <- rounds[[1]]
# comp_colors <- stringr::str_extract_all(string = test_game, pattern = 'red|blue|green')
# comp_counts <- stringr::str_extract_all(string = test_game, pattern = '\\d+')

# test_colors <- comp_colors[[1]]
# test_counts <- comp_counts[[1]]
# names(test_counts) <- test_colors

count_slowly <- \(rounds) {
  res <- vector(mode = 'list', length = length(rounds))
  for (i in seq_along(along.with = rounds)) {
    round <- rounds[[i]]
    colors <- stringr::str_extract_all(string = round,
                                       pattern = 'red|blue|green')
    counts <- stringr::str_extract_all(string = round,
                                       pattern = '\\d+')
#    names(counts) <- colors
#    res[[i]] <- counts
#    names(res[[i]]) <- colors
#    names(res[i]) <- paste0('round ', as.character(i))
  }
  res
}

# count_slowly(rounds = rounds[1])
# nooooo

test <- count_slowly(rounds = rounds[[1]])
```

```{r}
test_rounds <- rounds[1]
class(test_rounds)
test_rounds[[1]][2]
```

```{r}
test_color[[1]]
test_count[[1]]
wrapr::named_map_builder(targets = test_color[[1]], values = test_count[[1]])
```
Okay...

Wait, where did those come from???


```{r}
split_color <- \(round) {
  res <- stringr::str_split(string = round, pattern = ', ')
  res
}

test_game <- split_color(rounds[[1]])
test_count <- str_extract_all(string = test_game, pattern = '\\d+')
test_color <- str_extract_all(string = test_game, pattern = 'red|blue|green')
```

```{r}
# lapply(X = rounds[], FUN = split_color) ## nooope
round_test <- wrapr::named_map_builder(targets = test_color[[1]],
                                       values = test_count[[1]])
# this will make `round_test['red']` give me what I want.
# at last.

games <- vector(mode = 'list', length = length(rounds))
for (i in seq_along(along.with = rounds)) {
  use <- rounds[[i]]
  game <- split_color(round = use)
  color <- stringr::str_extract_all(string = game,
                                    pattern = 'red|blue|green')
  count <- stringr::str_extract_all(string = game,
                                    pattern = '\\d+')
  for (x in seq_along(along.with = game)) {
    round <- wrapr::named_map_builder(targets = color,
                                      values = count)
    game[[x]] <- round
  }
  game
}

```

Oh nope absolutely not. Not that. Ooookay.

```{r}
split_color <- \(round) {
  res <- stringr::str_split(string = round, pattern = ', ')
}

test_game <- split_color(rounds[[1]])
test_count <- str_extract_all(string = test_game, pattern = '\\d+')
test_color <- str_extract_all(string = test_game, pattern = 'red|blue|green')
round_test <- wrapr::named_map_builder(targets = test_color[[1]],
                                       values = test_count[[1]])
# this will make `round_test['red']` give me what I want.
# at last.

```

So I want to have... Game = x, round = y, red = round['red'], green = round['green'], blue = round['blue'].

...iff exists(round['color']).

```{r}
#Using test_game per above

l <- length(test_game)
test_count <- str_extract_all(string = test_game, 
                              pattern = '\\d+')
test_color <- str_extract_all(string = test_game, 
                              pattern = 'red|blue|green')
res <- data.table(game = rep(1, l),
                  round = seq_along(along.with = test_game),
                  red = 0,
                  green = 0,
                  blue = 0)
for (i in seq_along(along.with = test_game)) {
  round <- wrapr::named_map_builder(targets = test_color[[i]],
                                    values = test_count[[i]])
#  print(round['red'])
#  print(test_game[[i]])
  r <- as.numeric(round['red'])
  g <- as.numeric(round['green'])
  b <- as.numeric(round['blue'])
#  if (r > 0) { #res[round == i, red := round['red']]
#    print(r)
#  res[round == i, red := r]
  res[round == i, `:=` (red = r,
                        green = g,
                        blue = b)]
#  }
}
```
# okay here we go

```{r}
games <- readLines(con = here::here('data', 'day_02'))
names(games) <- 1:100
games <- stringr::str_remove_all(string = games, pattern = 'Game \\d+: ')
rounds <- stringr::str_split(string = games, pattern = '; ')

count_rounds <- \(games) {
  res <- data.table::data.table(game = numeric(),
                                round = numeric(),
                                red = numeric(),
                                green = numeric(),
                                blue = numeric())
  for (i in seq_along(along.with = games)) {
    rounds <- stringr::str_split(string = games[[i]], pattern = ', ')
    l <- length(rounds)
    colors <- str_extract_all(string = test_game, 
                              pattern = 'red|blue|green')
    counts <- str_extract_all(string = test_game, 
                              pattern = '\\d+')
    game <- data.table::data.table(game = i,
                                   round = seq_along(along.with = rounds),
                                   red = 0,
                                   green = 0,
                                   blue = 0)
    for (x in seq_along(along.with = rounds)) {
      round <- wrapr::named_map_builder(targets = colors[[x]],
                                        values = counts[[x]])
      r <- as.numeric(round['red'])
      g <- as.numeric(round['green'])
      b <- as.numeric(round['blue'])
      game[round == x, `:=` (red = r,
                             green = g,
                             blue = b)]
    }
    res <- poorman::bind_rows(res, game)
  }
  res
}
```
```{r}
suppressWarnings(count_rounds(games = rounds))
```

